---
title: "Simple document"
author: Jiayi
date: 2022-9-18
output: github_document
---
```{r message=FALSE}
library(tidyverse)
```

I'm an R Markdown document! 

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~
Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

* Bulleted list item 1

* Item 2

  * Item 2a

  * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header | Third Header
------------- | ------------- | -------------
Content Cell  | Content Cell  | Content Cell
Content Cell  | Content Cell  | Content Cell

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp),2)`.

# Section 3
### Plot from last time
This is going to make a plot. First I generate a dataframe, then use `ggplot` to make a scatterplot.
```{r chunk_label,echo=FALSE}
plot_df = tibble(
  x = rnorm(1000),
  y = 1 + 2 * x^2 + rnorm(1000)
)
ggplot(plot_df,aes(x=x,y=y))+geom_point()
```

### Plot from Learning Assignment
```{r}
dt = tibble(
  var_numeric = rnorm(n=500,mean=1),
  var_logic = var_numeric>0,
  var_abs = abs(var_numeric)
)
ggplot(dt,aes(x=var_abs))+geom_histogram()
```
The median value is `r round(median(dt$var_abs),2)`
